Extended Data

### 2021-09-17 doc/manuscript/Dow_manuscript_Nature.Rmd
reword results content so it's easier to read

For both ring- and diffuse- porous species at both sites, warmer $T_{max}$ in the critical temperature window resulted in earlier achievement of growth milestones (Figs. `r schematic_summary`, `r EDF_pheno_Tmax_climwin`).
Consistent with findings from previous studies[@parmesan_globally_2003, @ibanez_forecasting_2010,@friedl_tale_2014], at our focal sites the DOY of leaf greenup (measured at ecosystem level via remote sensing) advanced with increasing $T_{max}$ during the critical temperature window (p=0.001). 
Specifically, greenup DOY advanced 4.5 days/$^\circ$C at SCBI and 2.4 days/ $^\circ$C at Harvard Forest when comparing the years with the warmest and coldest mean $T_{max}$ during the critical temperature window, and mid-greenup also advanced, but to a lesser extent (Fig. `r DOY_timing`).
Similarly, $DOY_{25}$ (SCBI: RP = -1.9 days/ $^\circ$C, DP = -3.5 days/$^\circ$C , HF: RP = -2.8 days/$^\circ$C, DP = -7.9 days/$^\circ$C ), $DOY_{50}$ (SCBI: RP = -1.5 days/ $^\circ$C, DP = -3.5 days/$^\circ$C, HF: RP =  -5.0 days/$^\circ$C, DP = -7.3 days/$^\circ$C), and $DOY_{75}$ (SCBI: RP = -1.1 days/$^\circ$C, DP = -3.6 days/$^\circ$C , HF: RP = -7.2 days/$^\circ$C, DP= -6.6 days/$^\circ$C) at both sites all decreased with mean $T_{max}$ during the critical temperature window during the critical temperature window (Figs. `r schematic_summary`, `r DOY_timing`; see also Extended Data Figures `r EDF_pheno_Tmax_climwin`-`r EDF_pheno_Tmin_AprilMay`).

@@

The patterns observed at our focal sites were mirrored across an additional `r n_chronologies-n_chronologies_SCBI-n_chronologies_HF` chronologies from `r n_cores_sites-2` sites (Fig. `r tree_rings`; `r EDF_map`)[@dorangeville_drought_2018].
In total, our analysis included `r_n_chronologies` species at sites distributed from Alabama (Lat = 34.35) to Michigan (Lat = 45.56) and spanning a 15 $^\circ$C range in ~CTW~ April $T_{max}$ (**Cam, please confirm this change**).
Across all chronologies (focal sites included), RWI was significantly positively correlated with April $T_{max}$ for only 1% of records: 1 of 142 ring-porous and 2 of 66 diffuse-porous species-site combinations.
In contrast, RWI was frequently significantly negatively correlated with $T_{max}$ during peak growing season months (May-August), with significant correlations for 53% (Aug = 57, Jul = 90, Jun = 108, May = 47) and 46% (Aug = 22, Jul = 37, Jun = 53, May = 11) of species-site-month combinations for ring-porous and diffuse-porous species, respectively.
Again, $T_{min}$ generally exerted less influence over annual growth than $T_{max}$ (`r EDF_tree_rings_TMIN`), with few significant correlations between spring $T_{min}$ and RWI.

>>>>

For both ring- and diffuse- porous species at both sites, warmer $T_{max}$ in the critical temperature window resulted in earlier achievement of growth milestones (Figs. `r schematic_summary`, `r EDF_pheno_Tmax_climwin`).
Consistent with findings from previous studies[@parmesan_globally_2003, @ibanez_forecasting_2010,@friedl_tale_2014], at our focal sites the DOY of leaf greenup (measured at ecosystem level via remote sensing) advanced with increasing $T_{max}$ during the critical temperature window (p=0.001). 
Specifically, greenup DOY advanced 4.5 days/$^\circ$C at SCBI and 2.4 days/ $^\circ$C at Harvard Forest when comparing the years with the warmest and coldest mean $T_{max}$ during the critical temperature window, and mid-greenup also advanced, but to a lesser extent (Fig. `r DOY_timing`).
Similarly, at both sites, $DOY_{25}$, $DOY_{50}$, $DOY_{75}$, and $DOY_{g_{max}}$ all decreased with mean $T_{max}$ during the critical temperature window during the critical temperature window (Figs. `r schematic_summary`, `r DOY_timing`; see also Extended Data Figures `r EDF_pheno_Tmax_climwin`-`r EDF_pheno_Tmin_AprilMay`).
Specifically, at SCBI, RP growth advanced 1.9, 1.5, and 1.1 days/ $^\circ$C for $DOY_{25}$, $DOY_{50}$, and $DOY_{75}$, respectively, while DP growth advanced 3.5, 3.5, and 3.6 days/ $^\circ$C for $DOY_{25}$, $DOY_{50}$, and $DOY_{75}$, respectively.
At HF, RP growth advanced 2.8, 5.0, and 7.2 days/ $^\circ$C for $DOY_{25}$, $DOY_{50}$, and $DOY_{75}$, respectively, while DP growth advanced 7.9, 7.3, and 6.6 days/ $^\circ$C for $DOY_{25}$, $DOY_{50}$, and $DOY_{75}$, respectively.

@@

The patterns observed at our focal sites were mirrored across an additional `r n_chronologies-n_chronologies_SCBI-n_chronologies_HF` chronologies from `r n_cores_sites-2` sites (Fig. `r tree_rings`; `r EDF_map`)[@dorangeville_drought_2018].
In total, our analysis included `r_n_chronologies` species at sites distributed from Alabama (Lat = 34.35) to Michigan (Lat = 45.56) and spanning a 15 $^\circ$C range in ~~CTW~~ April $T_{max}$ (**Cam, please confirm this change**).
Across all chronologies (focal sites included), RWI was significantly positively correlated with April $T_{max}$ for only 1% of records: 1 of 142 ring-porous and 2 of 66 diffuse-porous species-site combinations.
In contrast, RWI was frequently significantly negatively correlated with $T_{max}$ during peak growing season months (May-August), with significant correlations for 53% (Aug = 57, Jul = 90, Jun = 108, May = 47) and 46% (Aug = 22, Jul = 37, Jun = 53, May = 11) of species-site-month combinations for ring-porous and diffuse-porous species, respectively.
Again, $T_{min}$ generally exerted less influence over annual growth than $T_{max}$ (`r EDF_tree_rings_TMIN`), with few significant correlations between spring $T_{min}$ and RWI.
